Tidal Locking in Low-Mass Stellar Binary Stars

### 2018-11-12 Paper/sync.tex
Updates from ShareLaTeX

Due to the discontinuities in the equilibrium tidal model equations, for example in Eq.~(\ref{eqn:cpl:eps}) when $\omega \approx n$, numerical solutions for the CPL and CTL models can produce unphysical evolution. We follow \citet{Barnes2013} and \citet{Fleming2018} and fix P$_{rot} = $ P$_{eq}$ according to Eq.~(\ref{eqn:cpl:eqPer}) or Eq.~(\ref{eqn:ctl:eqPer}) for the CPL and CTL models, respectively, when P$_{rot}$ is within $1\%$ of P$_{eq}$. We find that this scheme produces physically and numerically accurate results.

@@

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{../Plots/tidalExample.pdf}
   \caption{Tidal evolution of a 1 M$_{\odot} -$ 1 M$_{\odot}$ stellar binary's $e$ (top), P$_{orb}$ (middle) and P$_{rot}$ (bottom) for the CPL (blue) and CTL (orange) model. The blue (CPL) and orange (CTL) vertical dashed lines denote when the stellar binary tidally-locks. Both the CPL and CTL model predict the same qualitative evolution. The rotational evolution differs, however, as under the CPL model, the binary tidally-locks into a synchronous orbit as $e < \sqrt{1/19}$, e.g. Eq.~(\ref{eqn:cpl:eqPer}), while the CTL model predicts supersyncronous rotation due to the CTL model's equilibrium period eccentricity dependence (see Eq.~(\ref{eqn:ctl:eqPer})).}%
    \label{fig:tidalExample}%
\end{figure}

@@

%% SECTION: Simulations + Initial conditions %%

\section{Simulations} \label{sec:simulations}

@@

@@

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/qTauPorbLockHist.pdf}
   \caption{Caption}%
    \label{fig:qTauLock}%
\end{figure*}

@@

\subsection{Tidal-Locking as a Function of Eccentricity} \label{sec:results:ecc}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/eccPorbLockHist.pdf}
   \caption{Caption.}%
    \label{fig:eccLock}%
\end{figure*}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/eccPorbRatioHist.pdf}
   \caption{Caption.}%
    \label{fig:eccRatio}%
\end{figure*}

\subsubsection{Tidal-Locking as a Function of P$_{orb}$} \label{sec:results:porb}

\begin{figure}[h]
	\includegraphics[width=0.4\textwidth]{../Plots/lockTimePorbHist.pdf}
   \caption{Caption.}%
    \label{fig:lockHistPorb}%
\end{figure}

\subsection{Comparison with \kepler} \label{sec:kepler}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/lurie.pdf}
   \caption{Caption.}
    \label{fig:lurie}
\end{figure*}

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:binGyro}%
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCPL.pdf}
   \caption{Caption}%
    \label{fig:lockingCPL}%
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCTL.pdf}
   \caption{Caption}%
    \label{fig:lockingCTL}%
\end{figure}

%% SECTION: DISCUSSION %%

\section{Discussion} \label{sec:discussion}

>>>>

Due to the discontinuities in the equilibrium tidal model equations, for example in Eq.~(\ref{eqn:cpl:eps}) when $\omega \approx n$, numerical solutions for the CPL and CTL models can produce unphysical evolution. We follow \citet{Barnes2013} and \citet{Fleming2018} and fix P$_{rot} = $ P$_{eq}$ according to Eq.~(\ref{eqn:cpl:eqPer}) or Eq.~(\ref{eqn:ctl:eqPer}) for the CPL and CTL models, respectively, when two conditions are met: P$_{rot}$ is within $1\%$ of P$_{eq}$ and the P$_{rot}$ derivative points towards $P_{eq}$ on both sides of P$_{eq}$, i.e. when the gradient of P$_{rot}$ points towards the tidally-locked state when tides overpower magnetic braking. We find that this scheme produces physically and numerically accurate results.

@@

\begin{figure}
	\includegraphics[width=0.4\textwidth]{../Plots/tidalExample.pdf}
   \caption{Tidal evolution of a 1 M$_{\odot} -$ 1 M$_{\odot}$ stellar binary's $e$ (top), P$_{orb}$ (middle) and P$_{rot}$ (bottom) for the CPL (blue) and CTL (orange) model. The blue (CPL) and orange (CTL) vertical dashed lines denote when the stellar binary tidally-locks. Both the CPL and CTL model predict the same qualitative evolution. The rotational evolution differs, however, as under the CPL model, the binary tidally-locks into a synchronous orbit as $e < \sqrt{1/19}$, e.g. Eq.~(\ref{eqn:cpl:eqPer}), while the CTL model predicts supersyncronous rotation due to the CTL model's equilibrium period eccentricity dependence (see Eq.~(\ref{eqn:ctl:eqPer})).}%
    \label{fig:tidalExample}%
\end{figure}

@@

%% SECTION: Simulations + Initial conditions %%
\section{Simulations} \label{sec:simulations}

@@

\subsection{Coupled Stellar-Tidal Evolution}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption.}%
    \label{fig:coupledExample}%
\end{figure}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/eqPer.pdf}
   \caption{Caption.}%
    \label{fig:eqPer}%
\end{figure}

@@

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/qTauPorbRatioHist.pdf}
   \caption{Caption}%
    \label{fig:qTauLock}%
\end{figure*}

@@

@@

@@

\begin{figure}[t]
	\includegraphics[width=\textwidth]{../Plots/protDist.pdf}
   \caption{Caption}%
    \label{fig:protDist}%
\end{figure}

%% SECTION: COMPARISON TO KEPLER %%
\section{Comparison to \kepler} \label{sec:kepler}

\begin{figure}[t]
	\includegraphics[width=\textwidth]{../Plots/lurieFig7.pdf}
   \caption{Caption}%
    \label{fig:lurie7}%
\end{figure}

\subsection{The Subsynchronous Population} \label{sec:subsync}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/subsync.pdf}
   \caption{Caption}%
    \label{fig:subsync}%
\end{figure}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/subsyncTauHist.pdf}
   \caption{Caption}%
    \label{fig:subsyncTauHist}%
\end{figure}

\subsection{$Q$, $\tau$ Constraints from P$_{orb}$ and P$_{rot}$} \label{sec:qTau}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/porbProtPorbQHist.pdf}
   \caption{Caption}%
    \label{fig:qmap}%
\end{figure}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/porbProtPorbTauHist.pdf}
   \caption{Caption}%
    \label{fig:taumap}%
\end{figure}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/qLurie.pdf}
   \caption{Caption}%
    \label{fig:qLurie}%
\end{figure}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/tauLurie.pdf}
   \caption{Caption}%
    \label{fig:tauLurie}%
\end{figure}

%% SECTION: DISCUSSION %%
\section{Discussion} \label{sec:discussion}
